Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-23 paper/ijcai/paper.tex
new table
pass on RQ2

		\bottomrule
	\end{tabular}
	\caption {\ds{} reduction, as percentages. Higher is better.}
	\label{tab:red}
\end{table}
\normalsize

@@

@@

A fundamental issue of purely dynamic slicing techniques, critical
slicing in particular, is the risk of discarding faulty statements
(see Section~\ref{sec:slicing}). This research question evaluates the
practical impact of this conceptual issue. Table~\ref{table:fsws}
presents the number of faults where at least one of the faulty
statements appears in the final reports.\Mar{$\leftarrow$this seems a
  sensible choice that needs reasonable (to-the-point)
  justification. is there a rationale for this?  if not, was this
  choice used in other study? if yes, just say it was used and cite.}
More precisely, we look for faulty statements in the top 5 and 10 most
suspicious classes (as per the file ranking).

\Mar{CRITICAL: Sofia, I am really confused here. Is there a reason for
  why you chose not to show the proportion of cases where **DS** (not
  SFL(k) or \combpar{k}) includes the faulty statement? Wouldn't it be
  sufficient and simpler/clearer answering this question in terms of
  DS for k=5,10? (Note that the question is about DS.) On a similar
  note, considering this metric, I don't understand how SFL(k) can
  produce different result compared to \combpar{k}. I thought the
  difference in this case would only be the position in the
  ranking. This is counter-intuitive and needs a good explanation.}
Table~\ref{table:fsws} compares \sfl{}$^{k}$ and \combpar{k} with
respect to the metric number of cases where a faulty statement appears
in the ranking. Results show that \combpar{k} finds the faulty
statements \Fix{faster}\Mar{faster? chose another word.} than
\sfl{}$^{k}$.\Mar{I will revise the rest of this par. when I
  understand what is going on here...}  \sfl{}$^{5}$ finds $207$
($79.6\%$) faults whereas \combpar{5} finds $227$ ($87.3\%$) faults
for $k=5$, i.e., \combpar{5} misses $20$ ($7.7\%$) less faults
compared to \sfl{}$^{5}$. \sfl{}$^{10}$ finds $217$ ($83.5\%$) faults
whereas \combpar{10} finds $237$ ($91.2\%$) for $k=10$, i.e.,
\combpar{10} misses less $20$ ($7.7\%$) faults than
\sfl{}$^{10}$. There is also a significant difference within each
technique. Generally, the majority of faulty statements are found on
the $5$ highest ranked faulty classes. There are few cases where the
faulty statements are only found if the approach considers the first
$10$ highest ranked faulty classes \combpar{10} is the variant of our
approach that performs better \textbf{missing only 23 out of 260
  (8.8\%) cases}.

>>>>

		\bottomrule
	\end{tabular}
	\caption {\ds{} reduction in file size (percentages). Higher is better.}
	\label{tab:red}
\end{table}
\normalsize

@@

        \lang{}            & 100 & 96.9\\
        \cmath{}           & 89.4 & 95.2\\
        %\closure{}          &  & \\
		\chart{}			& 76.9 & 84.6 \\
        \jtime{}            & 81.5 & 85.2\\
        \mockito{}          & 71.1 & 78.9\\

		\bottomrule
	\end{tabular}
	\caption {\ds{} performance on capturing faulty statements, as percentages.}
	\label{tab:red}
\end{table}
\normalsize

@@

A fundamental issue of purely dynamic slicing techniques is the risk
of discarding faulty statements (see Section~\ref{sec:slicing}). This
research question evaluates the practical impact of this conceptual
issue. Table~\ref{tab:ds-cases-captured} shows the number of cases
dynamic slicing captures at least one of the faulty statements among
the sliced files for different values of $k$. These numbers indicat
that \Fix{...elaborate...}

        \lang{}            & - & -\\
        \cmath{}           & - & -\\
        %\closure{}          &  & \\
		\chart{}			& - & - \\
        \jtime{}            & - & -\\
        \mockito{}          & - & -\\

		\bottomrule
	\end{tabular}
	\caption {Percentages of cases \ds{} captures faults. Higher is better.}
	\label{tab:ds-cases-captured}
\end{table}
\normalsize

%% Table~\ref{table:fsws} presents the number of faults where at
%% least one of the faulty statements appears in the final
%% reports.\Mar{$\leftarrow$this seems a sensible choice that needs
%%   reasonable (to-the-point) justification. is there a rationale for
%%   this?  if not, was this choice used in other study? if yes, just say
%%   it was used and cite.}  More precisely, we look for faulty
%% statements in the top 5 and 10 most suspicious classes (as per the
%% file ranking).
%% \Mar{CRITICAL: Sofia, I am really confused here. Is there a reason for
%%   why you chose not to show the proportion of cases where **DS** (not
%%   SFL(k) or \combpar{k}) includes the faulty statement? Wouldn't it be
%%   sufficient and simpler/clearer answering this question in terms of
%%   DS for k=5,10? (Note that the question is about DS.) On a similar
%%   note, considering this metric, I don't understand how SFL(k) can
%%   produce different result compared to \combpar{k}. I thought the
%%   difference in this case would only be the position in the
%%   ranking. This is counter-intuitive and needs a good explanation.}

To analyze the impact of dynamic slicing in context, we also compared
\combpar{k} and \sfl{}$^{k}$ considering the same metric, \ie{}, the
number of cases the fault is captured by the technique. Note that the
reason \sfl{}$^{k}$ misses the fault is different compared to
\combpar{k}. It captures the fault if the fault is included within the
top $k$ files; it misses otherwise. Table~\ref{table:fsws} shows
results, indicating that \combpar{k} performs better than \sfl{}$^{k}$
on this metric.\Mar{my opinion is that we should not compare these two
techniques here: 1) it is not the goal of this RQ and 2) this is not
the best metric.} \sfl{}$^{5}$ finds $207$ ($79.6\%$) faults whereas
\combpar{5} finds $227$ ($87.3\%$) faults for $k=5$, i.e., \combpar{5}
misses $20$ ($7.7\%$) less faults compared to
\sfl{}$^{5}$. \sfl{}$^{10}$ finds $217$ ($83.5\%$) faults whereas
\combpar{10} finds $237$ ($91.2\%$) for $k=10$, i.e., \combpar{10}
misses less $20$ ($7.7\%$) faults than \sfl{}$^{10}$. There is also a
significant difference within each technique. Generally, the majority
of faulty statements are found on the $5$ highest ranked faulty
classes. There are few cases where the faulty statements are only
found if the approach considers the first $10$ highest ranked faulty
classes \combpar{10} is the variant of our approach that performs
better \textbf{missing only 23 out of 260 (8.8\%) cases}.
